\documentclass{jarticle}
\usepackage{robomech}
\usepackage{graphicx}
\usepackage{ikuo}%%便利コマンド集．
% \usepackage{siunitx}
\usepackage{jtygm}
\usepackage{bm}
\usepackage{balance}
\usepackage{amssymb}
% \usepackage{here}
\usepackage{amsmath}
\usepackage{url}
\usepackage[hang,small,bf]{caption}
\usepackage[subrefformat=parens]{subcaption}
% \usepackage{graphics} % for pdf, bitmapped graphics files
% \usepackage{epsfig} % for postscript graphics files
\newcommand{\FIGDIR}{./fig}
\newcommand{\ctext}[1]{\raise0.1ex\hbox{\textcircled{\scriptsize{#1}}}}
\setcounter{topnumber}{4} 

\begin{document}
\makeatletter
\title{立ち上がり時支援とエネルギー消費なしの中腰支援が可能な\\空気圧回生型ウェアラブル椅子}
{\vspace{-7 mm} }
{Pneumatic Regenerative Wearable Chair for \\
Supporting Up and a Half-sitting Posture without Energy Consumption}
{}

\author{
\begin{tabular}{ll}
    \hspace{1zw}　　長田京右（東京農工大）& 
    \hspace{1zw}森下克幸（東京農工大）\\
    ○正\hspace{1zw}水内郁夫（東京農工大）\\
 % ※協賛・後援団体の会員資格で発表される場合は「正・学」は不要です。
 \end{tabular}
 % &\\
 \vspace{1zh} \\
 \begin{tabular}{l}
{\small Kyosuke OSADA, TUAT, osada-rm25@mizuuchi.lab.tuat.ac.jp}\\
{\small Katsuyuki MORISHITA, TUAT, morishita@mizuuchi.lab.tuat.ac.jp}\\
{\small Ikuo MIZUUCHI, TUAT, ikuo@mizuuchi.lab.tuat.ac.jp}
\end{tabular}
}
\makeatother

\abstract{ \small 
Prolonged sitting and standing up at work is physically demanding.
The physical burden of long hours of sitting and standing up is great.
Assistive devices have been studied to reduce the physical burden.
The work that requires assistive devices is often performed outdoors, 
and it is difficult to obtain a power source. Therefore, long-term battery 
power operation is required. This study aims to develop a wearable pneumatic 
device that can support standing up and a half-sitting posture. Incorporating a 
pneumatic regeneration mechanism can reduce the physical burden and realize 
long-term operation.  We fabricated wearable chair to provide mid-back and 
stand-up support. In addition, the effectiveness of the pneumatic regeneration 
mechanism was verified through experiments.
}

\date{} % 日付を出力しない
\keywords{Long time operation, Air regeneration, Wearable chair}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

\small
% \input{chap_intro.tex}
% \input{teian.tex}
% \input{kaisei.tex}
% \input{compuressor.tex}
% \input{conclusion.tex}
% \input{chap_conclusion.tex}
\input{chap1}
\input{chap2}
\input{chap3}
\input{chap4}
\input{chap5}
\input{chap6}


\nocite{*}

\bibliography{reference}
\bibliographystyle{junsrt}

\normalsize
\end{document}
